---
title: "REVISED FINAL Action Seniors - CogFrailty Analyses (January 29, 2024)"
author: "RSF"
date: "2024-01-29"
output: 
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1) Data set-up and management

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(boot,MASS,readxl,mediation,psych,plyr,sandwich,ggplot2,lme4,lmerTest,rpart,survival,survminer,lsmeans,fmsb, mice, mitools, tableone,mgcv, nlme)


setwd("~/Desktop/Manuscripts/Ongoing Projects/ActionSeniors! Cognitive Frailty/")
data<-read_excel("ActionSeniors_CogsSPPB August 24, 2023.xlsx")#Data#

data$CogFrail<-NA
data$CogFrail[data$SPPB_1<=9 & data$MoCA_1<26]<-"Yes"
data$CogFrail[data$SPPB_1>9 | data$MoCA_1>=26]<-"No"

data$exclude<-0
data$exclude[data$ID==330]<-1

data$Group.1<-NA
data$Group.1[data$Group==0]<-"Interview"
data$Group.1[data$Group==1]<-"Otago"

data$Group_r[data$Group==0]<-1
data$Group_r[data$Group==1]<-0

data$Gender<-NA
data$Gender[data$Sex==1]<-0
data$Gender[data$Sex==2]<-1

data$Sex[data$Sex==1]<-"Female"
data$Sex[data$Sex==2]<-"Male"

#Create long data set
library(plyr)
wide<-rename(data,c("Weight_1"="Weightbaseline", "Height_1"="Heightbaseline","BMI_1"="BMIbaseline",
                    "Falls 12M prior to baseline"="Fallsbeforebaseline", "Total_Exposure"="TotalExposure",
                    "Total_Falls"="TotalFalls","PPA_1"="PPAbaseline","GDS_1"="GDSbaseline","MoCA_1"="MoCAbaseline",
                    "Trails_BA_1"="TrailsBAbaseline","DSST_1"="DSSTbaseline","TUG_1"="TUGbaseline",
                    "SPPB_1"="SPPBbaseline","Gait_Speed_1"="GaitSpeedbaseline","Trails_BA_2"="TrailsBA_2",
                    "Trails_BA_3"="TrailsBA_3","Group_r"="Group.r","Gait_Speed_2"="GaitSpeed_2","Gait_Speed_3"="GaitSpeed_3",
                    "Total Falls 6 Months"="TotalFalls6Months"))
detach("package:plyr", unload = TRUE)

wide$time<-1

wide2<-wide[c(1,71,66:70,2:12,65,15:18,29,31,34,45,47,50,61,63)]
data2 <- reshape(as.data.frame(wide2),idvar="ID",varying=c(26:31),direction="long",sep="_")
CogFrail<- subset(wide2, CogFrail=="Yes")
No_CogFrail<- subset(wide2, CogFrail=="No")
```


# 2) Compliance data set-up
Note: All analyses used estimated average compliance for Cognitively Frail participants (45.5%). High compliance is ≥ mean compliance for each group.

```{r}
setwd("~/Desktop/Manuscripts/Ongoing Projects/ActionSeniors! Cognitive Frailty/")
compliancedata<-read_excel("AS_compliance_August 24, 2023.xlsx") #Data#
library(plyr)
compliancedata2<-rename(compliancedata, c("Month 1"="OEPCOMP_1","Month 2"="OEPCOMP_2","Month 3"="OEPCOMP_3","Month 4"="OEPCOMP_4","Month 5"="OEPCOMP_5","Month 6"="OEPCOMP_6",
                                          "Month 7"="OEPCOMP_7","Month 8"="OEPCOMP_8","Month 9"="OEPCOMP_9","Month 10"="OEPCOMP_10","Month 11"="OEPCOMP_11","Month 12"="OEPCOMP_12"))
detach("package:plyr", unload = TRUE)

#Maximize compliance at 100% for each individual month
compliancedata2$OEPCOMP_1[compliancedata2$OEPCOMP_1>100]<-100
compliancedata2$OEPCOMP_2[compliancedata2$OEPCOMP_2>100]<-100
compliancedata2$OEPCOMP_3[compliancedata2$OEPCOMP_3>100]<-100
compliancedata2$OEPCOMP_4[compliancedata2$OEPCOMP_4>100]<-100
compliancedata2$OEPCOMP_5[compliancedata2$OEPCOMP_5>100]<-100
compliancedata2$OEPCOMP_6[compliancedata2$OEPCOMP_6>100]<-100
compliancedata2$OEPCOMP_7[compliancedata2$OEPCOMP_7>100]<-100
compliancedata2$OEPCOMP_8[compliancedata2$OEPCOMP_8>100]<-100
compliancedata2$OEPCOMP_9[compliancedata2$OEPCOMP_9>100]<-100
compliancedata2$OEPCOMP_10[compliancedata2$OEPCOMP_10>100]<-100
compliancedata2$OEPCOMP_11[compliancedata2$OEPCOMP_11>100]<-100
compliancedata2$OEPCOMP_12[compliancedata2$OEPCOMP_12>100]<-100


compliancedata2$AverageComply<-(compliancedata2$OEPCOMP_1 + compliancedata2$OEPCOMP_2 + compliancedata2$OEPCOMP_3 + compliancedata2$OEPCOMP_4 + compliancedata2$OEPCOMP_5 + compliancedata2$OEPCOMP_6 + compliancedata2$OEPCOMP_7 + compliancedata2$OEPCOMP_8+ compliancedata2$OEPCOMP_9 + compliancedata2$OEPCOMP_10 + compliancedata2$OEPCOMP_11 + compliancedata2$OEPCOMP_12)/12

wide3<- merge(compliancedata2,wide2, by = "ID")


OEP<-subset(wide3, CogFrail=="Yes")

#Determine compliant vs. non compiant for CogFrail and Non-Frail
describe(OEP$AverageComply) #Average compliance 45.5%

OEP2<-OEP[c(1,14:44)]

OEP2$Compliant<-NA
OEP2$Compliant[OEP2$AverageComply>=45.5] <- "Yes"
OEP2$Compliant[OEP2$AverageComply<45.5] <- "No"

OEP3<-OEP2[c(1,4:33,2)]
OEP4 <- reshape(as.data.frame(OEP3),idvar="ID",varying=c(25:30),direction="long",sep="_") 
```

# 3) Figure 1 - CONSORT Flow Chart Stratified by Cognitive Frailty Status

```{r}
#Determine CogFrail Status of Dropouts
CONSORT<- subset(wide2, ID==128 | ID== 131 | ID==132 | ID==134 | ID==158 | ID==163 | ID==176 | ID==185 | ID==192 | ID==195 | ID==213 | ID==214 | ID==216 | ID==220 | ID==222 | ID==223 |
                   ID==270 | ID==278 | ID==281 | ID==284 | ID==306 | ID==310 | ID==318 | ID==321 | ID==330 | ID==334 | ID==339 | ID==357 | ID==362 | ID==369 | ID==373 | ID==375 | ID==378 |
                   ID==385 | ID==395 | ID==398 | ID==407 | ID==408 | ID==412 | ID==413 | ID==424 | ID==426 | ID==427 | ID==428 | ID==432 | ID==438 | ID==455 | ID==461) #All dropouts

CONSORT<-CONSORT[c(1,3,8)]
MONTHS<- c(13,2,1,0,0,0,13,0,0,13,2,4,0,11,3,5,1,5,2,5,0,0,3,0,0,5,0,4,5,5,5,7,6,1,1,9,1,7,9,2,4,1,7,7,5,11,7,10) #Months in study before drop-out
CONSORT<-cbind(CONSORT,MONTHS) 

CONSORT$Group[CONSORT$Group==1]<-"INT"
CONSORT$Group[CONSORT$Group==0]<-"CON"

#Dropouts before 6 months (i.e., Month 7) or after 6 months in study
CONSORT$Timepoint<-NA
CONSORT$Timepoint[CONSORT$MONTHS<=7]<-"6 Months or Less"
CONSORT$Timepoint[CONSORT$MONTHS>7]<-"More than 6 Months"


#Sort by Group, Cognitive Frailty Status, and Time of Dropout
table(CONSORT$Timepoint,CONSORT$Group, CONSORT$CogFrail)
```

# 4) Table 1 - Participant Characteristics

Descriptive statistics for cognitively frail participants
```{r}
cogfrail_vars<-dput(names(wide2[c(10,9,14,20,21,15,23:25)]))

Table1_cogfrail_vars<-CreateTableOne(vars=cogfrail_vars, strata="Group", data=CogFrail)
print(Table1_cogfrail_vars,contDigits=2,missing=TRUE,quote=TRUE)
```

Descriptive statistics for non-cognitively frail participants
```{r}
Table1_nocogfrail_vars<-CreateTableOne(vars=cogfrail_vars, strata="Group", data=No_CogFrail)
print(Table1_nocogfrail_vars,contDigits=2,missing=TRUE,quote=TRUE)
```


# 5) Supplementary Material S1 - Differences in baseline characteristics by Cognitive Frailty status

```{r}
supp1_vars<-dput(names(wide2[c(10,9,14,20,21,15,23:25)]))
SuppTable1<-CreateTableOne(vars=supp1_vars, strata="CogFrail", data=wide2)
print(SuppTable1, contDigits=2, missing=TRUE, quote=TRUE)
```

# 6) Supplementary Material S2 - Differences in monthly compliance 

```{r}
Supp2graph<-wide3[c(1:13,16)]

#long form
compliancelong <- reshape(as.data.frame(Supp2graph),idvar="ID",varying=c(2:13),direction="long",sep="_")

#Maximize compliance at 100% (i.e., compliance cannot be greater than 100%, regardless of how many times/month OEP was completed)
compliancelong$OEPCOMP[compliancelong$OEPCOMP>100]<-100


compliancelong$Timepoint<-as.factor(compliancelong$time)

compliancelong.cogfrail<-subset(compliancelong, CogFrail=="Yes") 

comply.2<-lm(OEPCOMP~factor(time), compliancelong.cogfrail)
emms.2<-as.data.frame(lsmeans(comply.2, ~factor(time)))

Compliance.Graph<- emms.2 %>%
  ggplot() + geom_line(aes(x=time, y=lsmean)) +
  labs(x="Months", y="Monthy Adherence %") + ylim(0,100) + scale_x_continuous(breaks=seq(0,13,by=2)) +
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
Compliance.Graph
```


# 7) Table 2 - Primary and secondary outcomes at 12 months by treatment group for cognitively frail participants

## 7.1) Primary outcomes (Falls)

Falls Incident Rate Ratio at 12 months

```{r}
mdl.nb<-glm.nb(TotalFalls~Group.1+scale(Gender,scale=FALSE)+offset(log(TotalExposure/365)),subset(CogFrail,exclude==0)) 
print(summary(mdl.nb))
SE<-sqrt(diag(vcovHC(mdl.nb,"HC1")))
p=2*pnorm(-abs(coef(mdl.nb)/SE))
print(cbind(coef(mdl.nb),SE,p))
est<-cbind(Estimate=coef(mdl.nb),LL=coef(mdl.nb)-1.96*SE,UL=coef(mdl.nb)+1.96*SE)
exp_group<-exp(est)
print("Use these estimates and LL and UL for the 95% CI");exp_group
print("Significant effect of intervention on falls risk at 12 months for participants with CogFrailty")     
```

Falls Incident Rate Ratio at 6 months

```{r}
mdl2.nb<-glm.nb(TotalFalls6Months~Group.1+scale(Gender,scale=FALSE)+offset(log(TotalExposure/182.5)),subset(CogFrail,exclude==0)) 
print(summary(mdl2.nb))
SE<-sqrt(diag(vcovHC(mdl2.nb,"HC1")))
p=2*pnorm(-abs(coef(mdl2.nb)/SE))
print(cbind(coef(mdl2.nb),SE,p))
est<-cbind(Estimate=coef(mdl2.nb),LL=coef(mdl2.nb)-1.96*SE,UL=coef(mdl2.nb)+1.96*SE)
exp_group<-exp(est)
print("Use these estimates and LL and UL for the 95% CI");exp_group
print("Significant effect of intervention on falls risk at 6 months for participants with CogFrailty")     
```

Differences in total exposure based on group 

```{r}
exposurelm<-lm(TotalExposure~Group, subset(CogFrail, exclude==0))
lsmeans(exposurelm, ~Group)
contrast(lsmeans(exposurelm, ~Group), "trt.vs.ctrl", adj="none")
```

Differences in the cumulative number of falls by group

```{r}
setwd("~/Desktop/Manuscripts/Ongoing Projects/ActionSeniors! Cognitive Frailty/")
Monthly_falls <- read_excel("AS_Monthly falls_Mar 20 2019.xlsx")
Monthly_falls<-subset(Monthly_falls, ID %in% wide2$ID)

data1c<-cbind(Monthly_falls,wide2$CogFrail,wide2$Group)
data1c<-subset(data1c,ID!=330)

data1c<-plyr::rename(data1c,c("Month_1_Cumulative"="MonthCumulative_1","Month_2_Cumulative"="MonthCumulative_2","Month_3_Cumulative"="MonthCumulative_3",
                              "Month_4_Cumulative"="MonthCumulative_4","Month_5_Cumulative"="MonthCumulative_5","Month_6_Cumulative"="MonthCumulative_6",
                              "Month_7_Cumulative"="MonthCumulative_7","Month_8_Cumulative"="MonthCumulative_8","Month_9_Cumulative"="MonthCumulative_9",
                              "Month_10_Cumulative"="MonthCumulative_10","Month_11_Cumulative"="MonthCumulative_11","Month_12_Cumulative"="MonthCumulative_12",
                              "Month_13_Cumulative"="MonthCumulative_13","wide2$CogFrail"="CogFrail","wide2$Group"="Group"))
data1c_CogFrail_EX<-subset(data1c,Group==1 & CogFrail=="Yes")
data1c_CogFrail_UC<-subset(data1c,Group==0 & CogFrail=="Yes")
data1c_NoCogFrail_EX<-subset(data1c,Group==1 & CogFrail=="No")
data1c_NoCogFrail_UC<-subset(data1c,Group==0 & CogFrail=="No")

print("CogFrail Exercise");apply(data1c_CogFrail_EX[c(2:14)], 2, function(x) length(which(!is.na(x)))) #count people with falls data
print("CogFrail Usual Care");apply(data1c_CogFrail_UC[c(2:14)], 2, function(x) length(which(!is.na(x)))) #count people with falls data
print("No CogFrail Exercise");apply(data1c_NoCogFrail_EX[c(2:14)], 2, function(x) length(which(!is.na(x)))) #count people with falls data
print("No CogFrail Usual Care");apply(data1c_NoCogFrail_UC[c(2:14)], 2, function(x) length(which(!is.na(x)))) #count people with falls data

data1c.stacked<-reshape(data1c,idvar="ID",varying=c(2:27),direction="long",sep="_")
data1c.stacked$time<-data1c.stacked$time-1

Fallsmeans<-data.frame(aggregate(MonthCumulative~Group*CogFrail+time,data1c.stacked,sum))
subset(Fallsmeans, CogFrail=="Yes")
```

Estimated differences in falls per person-year at 12 months

```{r}
CogFrail$falls_ppy<-CogFrail$TotalFalls/(CogFrail$TotalExposure/365)

fallsppy_lm<-lm(falls_ppy~Group,  subset(CogFrail, exclude==0))
summary(fallsppy_lm)
lsmeans(fallsppy_lm, ~Group)
contrast(lsmeans(fallsppy_lm, ~~Group), "trt.vs.ctrl", adj="none")
```

Estimated differences in falls per person-year at 6 months

```{r}
CogFrail$falls_ppy_6mnths<-CogFrail$TotalFalls6Months/(CogFrail$TotalExposure/182.5)

fallsppy_6mnths_lm<-lm(falls_ppy_6mnths~Group,  subset(CogFrail, exclude==0))
summary(fallsppy_6mnths_lm)
lsmeans(fallsppy_6mnths_lm, ~Group)
contrast(lsmeans(fallsppy_6mnths_lm, ~~Group), "trt.vs.ctrl", adj="none")
```

Differences in exposure time

```{r}
expopsure_lm<-lm(TotalExposure~Group,  subset(CogFrail, exclude==0))
summary(expopsure_lm)
lsmeans(expopsure_lm, ~Group)
contrast(lsmeans(expopsure_lm, ~~Group), "trt.vs.ctrl", adj="none")
```

## 7.2) Secondary outcomes (Physical Function and Cognition)

Set-up for linear mixed models
```{r}
CogFrail_long <- reshape(as.data.frame(CogFrail),idvar="ID",varying=26:31,direction="long",sep="_")
CogFrail_long$timefactor<-as.factor(CogFrail_long$time)
```


SPPB (START HERE)

```{r}
SPPB_lm<-lmer(SPPB~Group.1*timefactor + scale(Gender,scale=FALSE) + SPPBbaseline + (1|ID),  subset(CogFrail_long, exclude==0))
anova(SPPB_lm)
lsmeans(SPPB_lm, ~Group.1|timefactor)
contrast(lsmeans(SPPB_lm, ~Group.1|timefactor), "trt.vs.ctrl", adj="none")
confint(contrast(lsmeans(SPPB_lm, ~Group.1|timefactor), "trt.vs.ctrl", adj="none"))
print("No significant effects")
```

Gait Speed

```{r}
GS_lm<-lmer(GaitSpeed~Group.1*timefactor + scale(Gender,scale=FALSE) + GaitSpeedbaseline + (1|ID),  subset(CogFrail_long, exclude==0))
anova(GS_lm)
lsmeans(GS_lm, ~Group.1|timefactor)
contrast(lsmeans(GS_lm, ~Group.1|timefactor), "trt.vs.ctrl", adj="none")
confint(contrast(lsmeans(GS_lm, ~Group.1|timefactor), "trt.vs.ctrl", adj="none"))
print("No significant effects for CogFrail participants")
```

MoCA

```{r}
emm_options(opt.digits = FALSE)

MoCA_lm<-lmer(MoCA~Group.1*timefactor + scale(Gender,scale=FALSE) + MoCAbaseline + (1|ID),  subset(CogFrail_long, exclude==0))
anova(MoCA_lm)
lsmeans(MoCA_lm, ~Group.1|timefactor)
contrast(lsmeans(MoCA_lm, ~Group.1|timefactor), "trt.vs.ctrl", adj="none")
confint(contrast(lsmeans(MoCA_lm, ~Group.1|timefactor), "trt.vs.ctrl", adj="none"))
print("No significant differences at 12 months")
```

# 8) Figure 2 - Accumulation of falls by treatment group for cognitively frail participants

```{r}
Fallsmeans$GroupCogFrail<-NA
Fallsmeans$GroupCogFrail[Fallsmeans$Group==0 & Fallsmeans$CogFrail=="Yes"]<-"Usual Care Group"
Fallsmeans$GroupCogFrail[Fallsmeans$Group==1 & Fallsmeans$CogFrail=="Yes"]<-"Exercise Group"

Fallsmeans.cogfrail<-subset(Fallsmeans, CogFrail=="Yes")

Cumulativefalls.Graph<- Fallsmeans.cogfrail %>%
  ggplot() + geom_line(aes(x=time, y=MonthCumulative, color=GroupCogFrail)) +
  labs(x="Months", y="Cumulative number of falls") + labs(color="Intervention Group") +
  scale_x_continuous(breaks=seq(0,13,by=1)) + scale_y_continuous(breaks=seq(0,300,by=50))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
Cumulativefalls.Graph
```

# 9) Table 3 - Primary and secondary outcomes at 12 months in exercise group based on cognitive frailty status and compliance to the intervention 


## 9.1) Primary outcomes (Falls)

Falls Incident Rate Ratio at 12 months (Cognitively Frail Participants)

```{r}
mdl.nb<-glm.nb(TotalFalls~Compliant+scale(Gender,scale=FALSE)+offset(log(TotalExposure/365)),subset(OEP2, exclude==0)) 
print(summary(mdl.nb))
SE<-sqrt(diag(vcovHC(mdl.nb,"HC1")))
p=2*pnorm(-abs(coef(mdl.nb)/SE))
print(cbind(coef(mdl.nb),SE,p))
est<-cbind(Estimate=coef(mdl.nb),LL=coef(mdl.nb)-1.96*SE,UL=coef(mdl.nb)+1.96*SE)
exp_group<-exp(est)
print("Use these estimates and LL and UL for the 95% CI");exp_group
print("No significant effect of compliance for CogFrail participants") 
```

Falls Incident Rate Ratio at 6 months (Cognitively Frail Participants)

```{r}
mdl.nb<-glm.nb(TotalFalls6Months~Compliant+scale(Gender,scale=FALSE)+offset(log(TotalExposure/182.5)),subset(OEP2, exclude==0)) 
print(summary(mdl.nb))
SE<-sqrt(diag(vcovHC(mdl.nb,"HC1")))
p=2*pnorm(-abs(coef(mdl.nb)/SE))
print(cbind(coef(mdl.nb),SE,p))
est<-cbind(Estimate=coef(mdl.nb),LL=coef(mdl.nb)-1.96*SE,UL=coef(mdl.nb)+1.96*SE)
exp_group<-exp(est)
print("Use these estimates and LL and UL for the 95% CI");exp_group
print("No significant effect of compliance for CogFrail participants") 
```


Falls Per Person-Year at 12 months (Cognitively Frail Participants)

```{r}
OEP2$falls_ppy<-OEP2$TotalFalls/(OEP2$TotalExposure/365)

fallsppy_comply<-lm(falls_ppy~AverageComply, OEP2)
summary(fallsppy_comply)
lsmeans(fallsppy_comply, ~AverageComply)
contrast(lsmeans(fallsppy_comply, ~~AverageComply), "trt.vs.ctrl", adj="none")
```

Falls Per Person-Year at 6 months (Cognitively Frail Participants)

```{r}
OEP2$falls_ppy_6mnths<-OEP2$TotalFalls6Months/(OEP2$TotalExposure/182.5)
OEP2$Avgcomply <- as.numeric(OEP2$AverageComply)


fallsppy_comply<-lm(falls_ppy_6mnths~Compliant, OEP2)
summary(fallsppy_comply)
lsmeans(fallsppy_comply, ~Compliant)
contrast(lsmeans(fallsppy_comply, ~~Compliant), "trt.vs.ctrl", adj="none")
```

## 9.2) Secondary outcomes (physical and cognitive function)

SPPB

```{r}
SPPB_lm<-lmer(SPPB~Compliant*factor(time) + scale(Gender,scale=FALSE) + SPPBbaseline + (1|ID), subset(OEP4, exclude == 0))
anova(SPPB_lm)
lsmeans(SPPB_lm, ~Compliant|factor(time))
contrast(lsmeans(SPPB_lm, ~Compliant|factor(time)), "trt.vs.ctrl", adj="none")
confint(contrast(lsmeans(SPPB_lm, ~Compliant|factor(time)), "trt.vs.ctrl", adj="none"))
print("Higher compliance among CogFrail participants was associated with better SPPB score at 12 months")
```

Gait Speed

```{r}
GS_lm<-lmer(GaitSpeed~Compliant*factor(time) + scale(Gender,scale=FALSE) + GaitSpeedbaseline + (1|ID), subset(OEP4, exclude == 0))
anova(GS_lm)
lsmeans(GS_lm, ~Compliant|factor(time))
contrast(lsmeans(GS_lm, ~Compliant|factor(time)), "trt.vs.ctrl", adj="none")
confint(contrast(lsmeans(GS_lm, ~Compliant|factor(time)), "trt.vs.ctrl", adj="none"))
print("No significant effects")
```

MoCA

```{r}
MoCA_lm<-lmer(MoCA~Compliant*factor(time) + scale(Gender,scale=FALSE) + MoCAbaseline + (1|ID), subset(OEP4, exclude==0))
anova(MoCA_lm)
lsmeans(MoCA_lm, ~Compliant|factor(time))
contrast(lsmeans(MoCA_lm, ~Compliant|factor(time)), "trt.vs.ctrl", adj="none")
confint(contrast(lsmeans(MoCA_lm, ~Compliant|factor(time)), "trt.vs.ctrl", adj="none"))
print("No significant differences")
```



# 10) Dose-response effect of adherence

## 10.1) Total Falls
```{r}
doseresponse.falls <- gam(TotalFalls ~ s(AverageComply), family = nb(),
              data = subset(OEP2, exclude == 0))

# Print summary of the GAM
summary(doseresponse.falls)

# Plot the dose-response curve
plot(OEP2$AverageComply, OEP2$TotalFalls, pch = 16) +
lines(OEP2$AverageComply, predict(doseresponse.falls, type = "response"), col = "purple")
```

## 10.2) Falls per person year
```{r}
doseresponse.fallsppy <- gam(falls_ppy ~ s(AverageComply), family = gaussian(),
              data = subset(OEP2, exclude == 0))

# Print summary of the GAM
summary(doseresponse.fallsppy)

# Plot the dose-response curve
plot(OEP2$AverageComply, OEP2$falls_ppy, pch = 16) +
lines(OEP2$AverageComply, predict(doseresponse.fallsppy, type = "response"), col = "purple")
```

## 10.3) MoCA
```{r}
doseresponse.MoCA <- lmer(MoCA~AverageComply + MoCAbaseline + (1|ID), data = OEP4)

# Print summary of the GAM
summary(doseresponse.MoCA)

# Plot the dose-response curve
doseresponse.MoCA.data <- expand.grid(
  AverageComply = seq(min(OEP4$AverageComply), max(OEP4$AverageComply), length.out = 100),
  MoCAbaseline = seq(min(OEP4$MoCAbaseline), max(OEP4$MoCAbaseline), length.out = 100)
)

  
predicted_response.MoCA <- predict(doseresponse.MoCA, newdata = doseresponse.MoCA.data, re.form = NA)
combined_data.MoCA <- data.frame(Dose = c(OEP4$AverageComply, doseresponse.MoCA.data$AverageComply),
                                 MoCAbaseline = c(OEP4$MoCAbaseline, doseresponse.MoCA.data$MoCAbaseline),
                                 Response = c(OEP4$MoCA, predicted_response.MoCA),
                                 Type = rep(c("Observed", "Fitted"), each = nrow(df)))

ggplot() +
  geom_smooth(data = subset(combined_data.MoCA, Type == "Fitted"), aes(Dose, Response)) +
  labs(x = "Average Compliance (%)",
       y = "MoCA Score") +
  theme_minimal()
```


## 10.4) SPPB
```{r}
doseresponse.SPPB <- lmer(SPPB~AverageComply + SPPBbaseline + (1|ID), data = OEP4)

# Print summary of the GAM
summary(doseresponse.SPPB)

# Plot the dose-response curve
doseresponse.SPPB.data <- expand.grid(
  AverageComply = seq(min(OEP4$AverageComply), max(OEP4$AverageComply), length.out = 100),
  SPPBbaseline = seq(min(OEP4$SPPBbaseline), max(OEP4$SPPBbaseline), length.out = 100)
)

  
predicted_response.SPPB <- predict(doseresponse.SPPB, newdata = doseresponse.SPPB.data, re.form = NA)
combined_data.SPPB <- data.frame(Dose = c(OEP4$AverageComply, doseresponse.SPPB.data$AverageComply),
                                 MoCAbaseline = c(OEP4$SPPBbaseline, doseresponse.SPPB.data$SPPBbaseline),
                                 Response = c(OEP4$SPPB, predicted_response.SPPB),
                                 Type = rep(c("Observed", "Fitted"), each = nrow(df)))

ggplot() +
  geom_smooth(data = subset(combined_data.SPPB, Type == "Fitted"), aes(Dose, Response)) +
  labs(x = "Average Compliance (%)",
       y = "SPPB Score") +
  theme_minimal()
```